At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-22 manuscript/supporting_info.tex
partial edits

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, 
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l m{10cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott2002} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1990}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Bek2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1996}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2016} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, 
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses. All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}. Further details for unpublished networks may be found there.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l l m{8cm} |}
    \hline
    Network & Network type & Country & Original source  \\
    \hline
    M\_PL\_001  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & Chile & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & Sweden & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
    M\_PL\_011  & Pollination & Mauritius & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Portugal (Azores) & \citep{Olesen2002a}  \\
    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & Greece (Athens) & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & Spain (Andalucia) & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & U.K. (England) & \citep{Memmott2002} \\
    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & Japan (Kyoto) & \citep{Kato1990}  \\
    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & New Zealand (South Island) & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & Venezuela & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & Venezuela & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l l m{6cm} |}
    \hline
    Network & Network type & Country & Original source \\
    \hline
    M\_PL\_032  & Pollination & U.S.A. (Illinois) & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & Canada (Ontario) & \citep{Small1976} \\
    M\_PL\_034  & Pollination & Chile & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & Jamaica & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Portugal (Azores) & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & Jamaica & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & Dominica & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & Denmark & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & Japan (Amami Islands) & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & Denmark (Greenland) & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & Denmark & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & Denmark & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & Denmark & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & Denmark & \citep{Bek2006}  \\
    M\_PL\_050  & Pollination & Spain (Canary Islands) & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & Argentina (R\'{i}o Negro) & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & Denmark (Greenland) & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & Japan (Kyusu) & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & Japan (Kyoto) & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & Japan (Fukui Prefacture) & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & Japan (Yamanashi) & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & Japan (Kibune) & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & Spain (Catalonia) & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & Brazil (Bu\'{i}que) & \citep{Bezerra2009} \\
    Basset  & Herbivory & Papua New Guinea & \citep{Basset1996}  \\
    Bl\"{u}thgen  & Herbivory & Malaysia (Sabah) & \citep{Bluthgen2006a}  \\
    Bodner  & Herbivory & Ecuador & \citep{Bodner2010}  \\
    Coley & Herbivory & Panama & \citep{Coley2006} \\
    Ibanez  & Herbivory & France (Central French Alps) & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & U.S.A. (Texas) & \citep{Joern1979} \\
    Novotny & Herbivory & Papua New Guinea & \citep{Novotny2012} \\
    Peralta & Herbivory & New Zealand (South Island) & \citep{Peralta2016} \\
    Sheldon & Herbivory & U.S.A. (Washington) & \citep{Sheldon1978} \\
    Ueckert & Herbivory & U.S.A. (Colorado) & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage
